

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}


 \hypersetup{
     colorlinks=true,
     linkcolor=red,
     filecolor=red,
     citecolor = black,      
     urlcolor=magenta,
     }


\usepackage{url}
\usepackage{bibentry}
\usepackage{natbib}
\usepackage[T1]{fontenc}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins


  
  
\begin{document}

  
\nobibliography{ref}
\bibliographystyle{abbrv}

  
  
\begin{center}
    {\huge Sashwat Tanay} \\ 
\end{center}



204 Lewis Hall   \hfill  \href{stanay@go.olemiss.edu}{stanay@go.olemiss.edu} \\
University of Mississippi   \hfill  \href{https://sashwattanay.github.io/sashwat_site}{sashwattanay.github.io/sashwat\_site}\\
University, MS 38677-1848, USA


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}


{\bf Ph.D. (Physics) } University of Mississippi \hfill {2016-2022}  \\
Dissertation advisor: Prof. Leo C. Stein  \\
Dissertation title: Post-Newtonian dynamics and waveforms of eccentric binary black holes 

{\bf B.Tech. (Mechanical Engineering) } Indian Institute of Technology Ropar \hfill {2009-2013}  \\

\end{rSection}



  
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

{\bf Teaching Assistant } University of Mississippi \hfill 2016-present  \\
\hspace*{1cm} Lab work and grading for Phys 221 and 222 (introductory physics) 


{\bf Junior Research Scholar} Tata Institute of Fundamental Research \hfill 2013-2015 


\end{rSection}
  
%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------



\begin{rSection}{Publications}
  \begin{enumerate}
  	\item \textbf{S. Tanay}, G. Cho, L. C. Stein. Action-angle variables of a binary black-hole with arbitrary eccentricity, spins and
masses at 1.5 post-Newtonian order (\textit{manuscript in progress})
  	\item G. Cho, \textbf{S. Tanay}, A. Gopakumar, H. M. Lee. Generalized quasi-Keplerian solution for eccentric, non-spinning compact binaries at
4PN order and the associated IMR waveform (\textit{submitted to Phys. Rev. D})
    \item \bibentry{Tanay:2020}
    \item \bibentry{Tanay:2019}
    \item \bibentry{Tanay:2016}
  \end{enumerate}
  \end{rSection}



 
%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS AND EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Research interests and experience}

\textbf{Past work:} \textbullet ~ Theoretical study of the dynamics of binary black holes (BHs) under the post-Newtonian Hamiltonian framework within
Einstein's general relativity (GR) \textbullet ~Modeling their trajectories and gravitational waves emitted by them in closed form \textbullet ~ Exploring
preliminary data analysis implications with these waveforms. \\
\textbf{Ongoing work:} \textbullet ~Studying the rate of change of quasi-normal mode frequencies of Kerr BHs with respect to their spins
 \textbullet ~Construct the power spectrum of scalar and tensor fluctuations sourced by many-field inflationary models of cosmology
 \textbullet ~Perform a Dirac-Hamiltonian constraint analysis for a higher-derivative theory of gravity beyond GR (the dynamical Chern-Simons gravity)
with the use of Dirac brackets

\end{rSection} 
  
  
  \pagebreak
 
   
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Computer skills}


\begin{itemize}
\item Mathematica, C/C++, Python, Matlab, Fortran, LaTeX, Jekyll, Bash
\item My contributions can be found at  \href{https://github.com/sashwattanay}{github.com/sashwattanay} 
\end{itemize}


\end{rSection}
  


%----------------------------------------------------------------------------------------
%	INVITED TALKS
%----------------------------------------------------------------------------------------

\begin{rSection}{Invited talks}


\begin{itemize}
\item Albert Einstein Institute Potsdam, ACR seminar \hfill Jun 2021
\item Simon Fraser University, Cosmology seminar \hfill Sep 2020
\item Indian Institute of Technology Ropar, Physics Department Colloquium \hfill Jan 2020
\end{itemize}


\end{rSection}





%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------

\begin{rSection}{Languages}


Hindi (native), English (fluent), German (elementary)


\end{rSection}



%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------

\begin{rSection}{References}


\begin{itemize}
\item Prof. Leo C. Stein\\University of Mississippi\\ \href{lcstein@olemiss.edu}{lcstein@olemiss.edu}
\item Prof. Emanuele Berti\\Johns Hopkins University\\ \href{berti@jhu.edu}{berti@jhu.edu}
\item Prof. Achamveedu Gopakumar\\Tata Institute of Fundamental Research, India\\ \href{gopu@tifr.res.in}{gopu@tifr.res.in}
\end{itemize}


\end{rSection}







\end{document}
